FTLR proof cases

### 2018-03-09 fully-abstract-comp/ftlr-proof-cases.tex
Discharge some easy cases.

\paragraph{Case: $\protect\tgeta{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tgetb{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tgete{\trg{r}}{\trg{r}}\mid$}

\paragraph{Case: $\protect\tgetlin{\trg{r}}{\trg{r}}$}

>>>>

\paragraph{Case: $\protect\tgeta{\trg{r}}{\trg{r}}$}
Similar to the case for $\tisptr{\trg{r}}{\trg{r}}$.

\paragraph{Case: $\protect\tgetb{\trg{r}}{\trg{r}}$}
Similar to the case for $\tisptr{\trg{r}}{\trg{r}}$.

\paragraph{Case: $\protect\tgete{\trg{r}}{\trg{r}}\mid$}
Similar to the case for $\tisptr{\trg{r}}{\trg{r}}$.

\paragraph{Case: $\protect\tgetlin{\trg{r}}{\trg{r}}$}
Similar to the case for $\tisptr{\trg{r}}{\trg{r}}$.
